### 2025-02-21 uw-ethesis-frontpgs.tex
edited
new

%   \noindent
% \begin{tabbing}
% Internal-External Member: \=  \kill % using longest text to define tab length
% Internal-External Member: \> John Smith \\
% \> Professor, Dept. of XX, University of ABC \\
% \end{tabbing}
%   \bigskip

%   \noindent
% \begin{tabbing}
% Internal-External Member: \=  \kill % using longest text to define tab length
% Other Member(s): \> John Smith \\
% \> Professor, Dept. of XX, University of ABC \\
% \end{tabbing}

@@

Extensive numerical experiments in this thesis demonstrate that the proposed methods substantially improve computational efficiency, sometimes shortening runtime by orders of magnitude compared to standard nested simulation procedures.
The results indicate that deep neural network metamodels with transfer learning can quickly adapt to new market scenarios and contract specifications.
This research contributes to the advancement of risk management practices for complex actuarial products and financial derivatives.
By leveraging advanced machine learning techniques, the thesis offers a practical and scalable solution for insurers to perform timely and accurate risk assessments.
The integration of long short-term memory metamodels and transfer learning into a nested simulation framework represents a major step forward toward more efficient, adaptable, and robust methodologies in actuarial science and quantitative finance.

@@

Additionally, I extend my sincere thanks to my best friends, who have stood by me during the most challenging times. 
Their unwavering support and encouragement have been a constant source of strength that has helped me overcome obstacles and maintain my motivation throughout this process. 
Words cannot fully convey how much their presence has meant to me over these years.

>>>>

  \noindent
\begin{tabbing}
Internal-External Member: \=  \kill % using longest text to define tab length
Internal-External Member: \> Yuying Li \\
\> Professor, School of Computer Science \\
\> University of Waterloo \\
\end{tabbing}
  \bigskip

  \noindent
\begin{tabbing}
Internal-External Member: \=  \kill % using longest text to define tab length
Other Member(s): \>  Emiliano Valdez \\
\> Professor, Dept. of Mathematics \\
\> University of Connecticut \\
\end{tabbing}

@@

Extensive numerical experiments in this thesis demonstrate that the proposed methods substantially improve computational efficiency, sometimes shortening runtime by orders of magnitude compared to standard nested simulation procedures.
The results indicate that deep neural network metamodels with transfer learning can quickly adapt to new market scenarios and contract specifications.
This research contributes to the advancement of risk management practices for complex actuarial products and financial derivatives.
By leveraging advanced machine learning techniques, this thesis offers a practical and scalable solution for insurers to perform timely and accurate risk assessments.
The integration of long short-term memory metamodels and transfer learning into a nested simulation framework represents a major step forward toward more efficient, adaptable, and robust methodologies in actuarial science and quantitative finance.

@@

Additionally, I extend my sincere thanks to my best friends.
Their unwavering support and encouragement have been a constant source of strength that has helped me overcome obstacles and maintain my motivation throughout this process. 
Words cannot fully convey how much their presence has meant to me over these years.
